Almost compatible functions and infinite length games

### 2016-02-03 articles/almost-compatible-functions-and-topological-games/article.tex
alan's revisions

\maketitle

@@

            \begin{lemma*} If $X\in M$ and $\dot x$ is a $\mathbb P$-name,
            then\label{easyname}
             there is a $\tau\subset X\times \mathbb P$, such that
            for any generic $G$, $\tau[G] = X\cap \val_G(\dot x)$.
            \end{lemma*}

@@

            \begin{lemma*}\cite{MR597342}
            Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a
             generic\label{factor} filter,
             and let $\lambda\in \omega_2$. Then the final model $M[G]$
            is equal to $(M[G_\lambda])[G^\lambda]$ in the sense that
            $G^\lambda$ is a $\operatorname{Fn}(\omega_2\setminus \lambda,
             2)$-generic filter   over the model $M[G_\lambda]$.

            In addition, for each $X\in M$ and name $\dot A\subset
            X\times \operatorname{Fn}(\omega_2,2)$, we get that
             \[ (\dot A(G_\lambda))[G^\lambda] = \dot A [G]\ \ \mbox{where}\
            \dot A(G_\lambda) =
             \{ (x,p\restriction [\lambda,\omega_2))  :
             (x,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \lambda\in G_\lambda\}
            \]
            \end{lemma*}

            With these lemmas in hand we are ready to prove the theorem. The idea
            of the proof comes from  Kunen's result about no $\omega_2$ length mod
            finite chains of subset of $\omega$. We consider any  family of
            names  of suitable one-to-one functions from countable subsets of
            $\omega_2$ into $\omega$. We identify a large enough $\lambda\in \omega_2$
            so that a pattern has emerged and we pass to the model $M[G_\lambda]$. We
            then show that this pattern can not continue out to $\omega_2$.

@@

             Now let $Y$ equal $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\setminus \lambda$. Furthermore,
             fix any $\mu\in \lambda\subset H$ such that
               $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\cap \lambda$ is contained in $\mu$.
             Let $\delta\in \omega_1$ denote the order type of
             $Y$ and let  $\varphi_{\mu,\lambda}$ be the order-preserving function
             from  $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts
             canonically to
            an order-preserving bijection $\varphi_{\mu,\lambda}:
            \operatorname{Fn}(\mu\cup Y,2) \mapsto
            \operatorname{Fn}(\mu+\delta,2)$.
            Now fix any  $\mu<\lambda$ so that
             $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\cap \lambda\subset \mu$.
            We can similarly make sense of the name
             $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_H$.
            Here simply, for each tuple $(\,(k,m), p)\in \dot
            f_{[\lambda,\lambda+\omega)}$,
             we have that $(\,(k,m),\varphi_{\mu,\lambda}(p))$ is in $F_H$.
            Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
            be interpreted in the above sense as giving $F_H$ (which is an element
            of $H$).

>>>>

\maketitle
\footnotetext[1]{The second author acknowledges support provided by
NSF-DMS 1501506}

@@

            \begin{lemma} If $X\in M$ and $\dot x$ is a $\mathbb P$-name,
            then\label{easyname}
             there is a $\tau\subset X\times \mathbb P$, such that
            for any generic $G$, $\tau[G] = X\cap \val_G(\dot x)$.
            \end{lemma}

@@

            \begin{lemma}\cite{MR597342}
            Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a
             generic\label{factor} filter,
             and let $\lambda\in \omega_2$. Then the final model $M[G]$
            is equal to $(M[G_\lambda])[G^\lambda]$ in the sense that
            $G^\lambda$ is a $\operatorname{Fn}(\omega_2\setminus \lambda,
             2)$-generic filter   over the model $M[G_\lambda]$.

            In addition, for each $X\in M$ and name $\dot A\subset
            X\times \operatorname{Fn}(\omega_2,2)$, we get that
             \[ (\dot A(G_\lambda))[G^\lambda] = \dot A [G]\ \ \mbox{where}\
            \dot A(G_\lambda) =
             \{ (x,p\restriction [\lambda,\omega_2))  :
             (x,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \lambda\in G_\lambda\}
            \]
            \end{lemma}

            With these lemmas in hand we are ready to prove the theorem. The idea
            of the proof comes from  Kunen's result about no $\omega_2$ length mod
            finite chains of subsets of $\omega$. We consider any  family of
            names  of suitable one-to-one functions from countable subsets of
            $\omega_2$ into $\omega$. We identify a large enough $\lambda\in \omega_2$
            so that a pattern has emerged and we pass to the model $M[G_\lambda]$. We
            then show that this pattern can not continue out to $\omega_2$.

@@

             Now let $Y$ equal $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\setminus \lambda$. Furthermore,
             fix any $\mu\in \lambda\subset H$ such that
               $\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\cap \lambda$ is contained in $\mu$.
             Let $\delta\in \omega_1$ denote the order type of
             $Y$ and let  $\varphi_{\mu,\lambda}$ be the order-preserving function
             from  $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts
             canonically to
            an order-preserving bijection $\varphi_{\mu,\lambda}:
            \operatorname{Fn}(\mu\cup Y,2) \mapsto
            \operatorname{Fn}(\mu+\delta,2)$.
            We can similarly make sense of the name
             $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_H$.
            Here simply, for each tuple $(\,(k,m), p)\in \dot
            f_{[\lambda,\lambda+\omega)}$,
             we have that $(\,(k,m),\varphi_{\mu,\lambda}(p))$ is in $F_H$.
            Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
            be interpreted in the above sense as giving $F_H$ (which is an element
            of $H$).
